---
title: "Power of Compounding"
author: "Jyoti Prakash"
date: "August 11, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Power of Compounding

The App simulates the growth of on initial investement with certain % of interest compounded annualy after certain years and compares it with simple/linear growth.

The App requires following input parameters

- Initial Investment in $ Millions
- No. of Years of Investment
- Annual Rate of Interest (%)

Following are the outputs

- Graphical comparision of compounded growth and linear growth.
- Final investment amount from both the growth models.

## UI.R Code

```{r UI, eval=FALSE,echo=TRUE}
library(shiny);library(ggplot2);library(plotly)

shinyUI(fluidPage(

  titlePanel("Power of Compounding"),
  
  sidebarLayout(
    sidebarPanel(
      numericInput("Amount", "Initial Investment ($ Millions)", 
                   value = 10, min = 1, max = 100, step = 1), 
      
      sliderInput("Year", "No. of Years of Investment",
                  min = 0,max = 30,value = 20),
      
      numericInput("Rate","Annual Rate of Interest (%)",
                   min = 0,max = 20,value = 10,step = .1),
      
      checkboxInput("show_CI", "Show/Hide Investment projections with Compounded growth", value = TRUE),
      
      checkboxInput("show_SI", "Show/Hide Investment projections with Simple/Linear growth", value = FALSE),
      
      h4("------------------------------"),
      h4("Instructions to use the app"),
      h5("Input the following"),
      h5("- Initial Investment in $ Millions"),
      h5("- No. of Years of Investment"),
      h5("- Annual Rate of Interest (%)")
      
    ),
    
    mainPanel(
      plotlyOutput("plot"),
      h4("Total value of investment (with compounded growth) - $M :"),
      textOutput("A"),
      h4("Total value of investment (with simple/linear growth) - $M :"),
      textOutput("B")
    )
  )
))

```
## Server.R Code

```{r SERVER, eval=FALSE,echo=TRUE}
library(shiny);library(ggplot2);library(plotly)

shinyServer(function(input, output) {
  
  output$plot <- renderPlotly({
    y <- 0:input$Year
    ACI <- 0:input$Year
    ASI <- 0:input$Year
    for (i in 0:input$Year+1) {
      ACI[i] <- input$Amount*(1+input$Rate/100)^y[i]
      ASI[i] <- input$Amount*(1+(input$Rate/100)*y[i])
    }
    
    data <- data.frame(y,ACI,ASI) 
    ## View(data)
    p <- plot_ly(data) %>%
      layout(title = 'Power of Compounding',
             xaxis = list(title = "Years of Investment",showgrid = TRUE,zeroline = TRUE),
             yaxis = list(side = 'left', title = 'Amount ($ Millons)',showgrid = TRUE, zeroline = TRUE),
             legend = list(x = 0.1, y = 0.9),
             hovermode="compare") %>%
      
      add_trace(x = ~y, y = ~ACI,type = 'scatter',visible=input$show_CI,mode="lines",name = 'Compounded growth',
                marker = list(color = "red"),
                hoverinfo = "text",
                text = ~paste("Amount ($M):",round(ACI,digits=1),"<br>Year:",y,"<br>Gain over Simple growth ($M):",round(ACI-ASI,digits=1))) %>%
      
      add_trace(x = ~y, y = ~ASI, type = 'scatter',visible=input$show_SI,mode="lines",name = 'Simple/linear growth',
                marker = list(color = "blue"),
                hoverinfo = "text",
                text = ~paste("Amount ($M):",round(ASI,digits=1),"<br>Year:",y))
    
    
    
  })
  
  output$A <- renderText({
    round(input$Amount*(1+input$Rate/100)^input$Year,digits = 1)
  })
  
  output$B <- renderText({
    input$Amount*(1+(input$Rate/100)*input$Year)
  })
  
})

```
## App Link

 [Power of Compounding](https://jprakash007.shinyapps.io/power_of_compouding/)


## Thank You

